\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../UTIL/Figures}}}
\begin{document}

The following assumptions are made in the analysis to bound the problem space:

\begin{enumerate}
    \item It is assumed that the needs and impacts of the various independent water companies that operate in the management catchment area, or otherwise abstract water from the Rivers Test and Itchen, are negligible compared to that of Southern Water
    \item It is assumed that the needs of areas outside of the management catchment (e.g. the Isle of Wight) remain static and can be modelled as constants.
    \item It is assumed that stakeholders respect local authorities, regulators, and other organisations
    \item It is assumed that shareholders in public water companies would not unreasonably withhold funding from them, and are not operating these companies illegally
    \item The debt held by public water companies is modelled monolithically
    \item The sewage and wastewater systems in the Management Catchment are not considered. This paper focuses on the systems concerning water supply in the region
    \item For water supply elements where sewage or wastewater is concern, the flow and processing of this is assumed to be static and monolithically modelled. 
    \item Only publicly available data can be used in this analysis.
    \item It is assumed that external water companies will not donate water from their abstraction to Southern Water.
    \item It is assumed that external water companies will not sell allowance from their abstraction licenses to Southern Water.
    \item It is assumed that population growth is a static rate and is constant.
    \item It is assumed that there are no legal obstacles to the recommendations.
    \item It is assumed that recommendations will be presented to one government (i.e. no cabinet reshuffle/elections occur at the same time).
    \item It is assumed that the regional authorities fall under HM Government elected in 2024, as some recommendations align with its policy.
    \item The effects of climate change not mentioned in this paper (rising sea levels etc.) are ignored.
    
\end{enumerate}
